---
title: "The Perks of Buliding a Website"
author: "giacomo_bignardi"
date: "10/09/2019"
output: html_document
tags: [ "art","science"]
fig_caption: yes
hidden: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## BIO

<iframe src="https://giphy.com/embed/26u6dIwIphLj8h10A" width="480" height="480" frameBorder="0" class="giphy-embed" allowFullScreen></iframe><p><a href="https://giphy.com/gifs/26u6dIwIphLj8h10A">via GIPHY</a></p>

Giacomo Bignardi born in the humanities, with a degree in Drama, Art and Music Studies from the [University of Bologna](https://corsi.unibo.it/laurea/DAMS). He was then raised by scientists while doing a minor in [Brain and Mind](https://minor.vu.nl/nl/minoren/brain-and-mind), leaving home to research at the Complex Trait Genetic department at the [Vrije Universiteit](https://ctg.cncr.nl/) in Amsterdam. After, he tried to grow  up in London, studying Neuroaesthetics at [Goldsmiths, University of London](https://www.gold.ac.uk/pg/msc-psychology-arts-neuroaesthetics-creativity/), and collaborating with the NTR, at the [Biological Psychology Dept.](https://tweelingenregister.vu.nl/) (which is still in Amsterdam, he loves that city). 
All grown up, he is interested in aesthetics experiences, what they mean, and their underlying sources of etiological variation. Especially in the genetic ones.

This website is about the wanderings on the `science` and the `art` that surround the genetic architecture of aesthetic experiences.


Here you have a glimpse to what is importatnish (pinned tweet) for me at the moment:


```{r, echo = FALSE} 
#fdown here goes the tweet 
```

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">This year the poster &#39;Putting Genetics in Aesthetics&#39; won the best poster award at <a href="https://twitter.com/hashtag/VSAC2019?src=hash&amp;ref_src=twsrc%5Etfw">#VSAC2019</a> ! <a href="https://t.co/0WC49tMpLp">https://t.co/0WC49tMpLp</a><br><br>Super grateful to <a href="https://twitter.com/NTRscience?ref_src=twsrc%5Etfw">@NTRscience</a> <a href="https://twitter.com/SofiekeKevenaar?ref_src=twsrc%5Etfw">@SofiekeKevenaar</a> <a href="https://twitter.com/zenabtamimy?ref_src=twsrc%5Etfw">@zenabtamimy</a> and Dorret. To <a href="https://twitter.com/mscpanc?ref_src=twsrc%5Etfw">@mscpanc</a> and Becky. <br>And thanks to <a href="https://twitter.com/tincatwin?ref_src=twsrc%5Etfw">@tincatwin</a> who introduced me to BG 🙏</p>&mdash; giacomo bignardi (@GiacomoBIgnardi) <a href="https://twitter.com/GiacomoBIgnardi/status/1166607801617174529?ref_src=twsrc%5Etfw">August 28, 2019</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

## EDUCATION

<p style="text-align:left;">
    <strong>Goldsmiths University of London</strong>
    <span style="float:right;"> 
    September 2018-December 2019
    </span>
<a href = "https://www.gold.ac.uk/pg/msc-psychology-arts-neuroaesthetics-creativity/"><br>MSC IN PSYCHOLOGY OF THE ARTS, NEUROAESTHETICS AND CREATIVITY</br></a>
</p>


*Courses*: Advance Quantitative Method in Statistics, Aesthetic Science, Creativity, Creative Computing, Multivariate Statistics, Neuroscience, Research Design & Analysis, Research Skills, Workshop in Philosophy of Art for Cognitive Scientist

*Thesis*: Dissertation on behavioural genetics studies of aesthetics: *Putting genetics into aesthetics. Etiological Sources of Variation in Aesthetic Chills*. Under the supervision of [Rebecca Chamberlain](https://www.researchgate.net/profile/Rebecca_Chamberlain) and [Dorret I Boomsma](https://www.researchgate.net/profile/Dorret_Boomsma)

*Internship*: [NTR](https://tweelingenregister.vu.nl/), Dept.of Biological Psychology, VU Amsterdam


<p style="text-align:left;">
    <strong>Vrije Universiteit Amsterdam </strong>
    <span style="float:right;">
        September 2016-February  2017
    </span>
 <a href = "https://minor.vu.nl/nl/minoren/brain-and-mind"><br>MINOR IN BRAIN AND MIND</br></a>
</p>

*Courses*: Brain in trouble, Cognitive Neuroscience, Mind and Machine, Nature vs Nurture, The Developing Brain


<p style="text-align:left;">
    <strong>University of Bologna </strong>
    <span style="float:right;">
        September 2014-July 2017 
    </span>
    <a href = "https://corsi.unibo.it/laurea/DAMS"><br>BA IN DRAMA, ARTS AND MUSIC STUDIES</br></a>
</p>

*Courses*: Psychology of Art, Psychology of Music, Philosophy and Aesthetic of Music, Semiotics, Phenomenology of Styles, Film analysis, Theory and Tecnique of New Media, Film History, History of Photography, History of Theater, Contemporary Hystory, Italian Litterature, Calculus I, Calculus II, Chemistry, Physics's Laboratory, introduction to HTML


*Thesis*: Dissertation in psychological studies of the arts: *Why We Like What We Like. Genetic Influences on Individual Differences in the Intensity of Visual Aesthetic Experiences*. Under the supervision of [Stefano Ferrari](https://www.unibo.it/sitoweb/stefano.ferrari/en), [Tinca JC Polderman](https://www.researchgate.net/profile/Tinca_Polderman) and with the collaboration of [Luca Ticini](https://www.researchgate.net/profile/Luca_Ticini_Frsa)


*Internship*: Center for Neurogenomic and Cognitive Research, [CTG lab](https://ctg.cncr.nl/), VU Amsterdam

## RESEARCH

<p style="text-align:left;">
    <strong>Dept. of Biological Psychology, Amsterdam, Netherlands</strong>
    <span style="float:right;"> 
    June 2019 - July 2019
    </span>
<br>INTERN</br>
</p>

*Project*: Heritability of individual differences in the propensity of feeling aesthetic Chills. Supervised by [Dorret I Boomsma](https://www.researchgate.net/profile/Dorret_Boomsma)

*Role*: `data analyist`, `writer`

<p style="text-align:left;">
    <strong>Complex Trait Genetic Lab, Amstedam, Netherlands</strong>
    <span style="float:right;"> 
    March 2018-July 2018
    </span>
<br>VISITING RESEARCHER</br>
</p>

*Project*: Genetic influences on individual differences in the intensity of visual aesthetic experiences. Supervised by [Tinca JC Polderman](https://www.researchgate.net/profile/Tinca_Polderman) and in collaboration with [Dirk J Smit](https://www.researchgate.net/profile/Dirk_Smit)

*Role*: `data analyist`, `writer`

## SKILLS


```{r figs, echo=FALSE}
m <- matrix(c( 3, 0, 1, 1, 0, 0,
              21.5, 0, 1.5, 7.0, 10,0, 
              10, 2, 3, 0, 3, 0, 
              0, 0, 0, 0, 5, 0,
              4, 4, 4 ,4 ,4 ,0,
              0, 0, 0.5, 2, 1.5, 1 ),
            byrow = TRUE,
            nrow = 6, ncol = 6)
haircolors <- c("Programming","Inferential Statistics", "Generative Art", "WebDesign", "Creativity","Design")

groupColors <- c("#ea4a35", "#F05934", "#f4981f", "#F29743", "#F4A647", "#F2CF60")

dimnames(m) <- list(have = haircolors,
                    prefer = haircolors)
circlize::chordDiagram(m, groupColors, annotationTrack = c("name", "grid"),
             annotationTrackHeight = c(0.03, 0.01))
```

SKILLS \ref{fig:figs} *a Chord Diagram that should kind of represent my skills. Arches represent the relative weight of one skill onto the other. Every data used for this graph has been made up by myself. Further investigation are needed to prove their validity. As you can see I am quite creative. However, there are not any divergent thinking or C scores are out there to certify it. Graph made using the R package [Circlize](https://github.com/jokergoo/circlize). Color palette from the [RothkoViz](http://ereyes.net/rothkoviz/00-colors.html) project, No.12, 1954. 'cause I cried once in front of it.*

## EXPERIENCE

<p style="text-align:left;">
    <strong>VSAC 2019, Leuven, Belgium</strong>
    <span style="float:right;"> 
    August 2019
    </span>
   <br> <a href="https://www.researchgate.net/publication/335352770_Putting_Genetics_in_Aesthetics_Etiological_Sources_of_Variation_in_Aesthetic_Chills">PRESENTER</a>,<a href="https://www.researchgate.net/publication/335353025_Degrees_of_Freedom_Genetic_Environment_and_Generative_Art"> SPEAKER</br></a>
</p>

*Poster Presentation*: Putting Genetics in Aesthetics: Etiological Sources of Variation in Aesthetic Chills.Winner of the best poster award

*Talk*: Degrees of Freedom: Genetic, Environment, and Generative Art

<p style="text-align:left;">
    <strong>Art and Science Relationship Conference, Oxford, UK</strong>
    <span style="float:right;"> 
    May 2019
    </span>
  <a href="https://www.facebook.com/385058852329692/photos/ms.c.eJwtycEJADAMAsCNCklUdP~;FQkufx6FHlGAoqT54tlkjkt~;p~_zYW5~;kJtA~-~-.bps.a.423656635136580/423656928469884/?type=3&theater"> <br>SPEAKER</br></a>
</p>

</p>

*Talk*: Neuroscience of aesthetics and Art of Science: Degrees of Freedom. Interrogating the Art-Science Relationship Conference. Visual art and neuroscience section

<p style="text-align:left;">
    <strong>VSAC 2018, Trieste, Italy</strong>
    <span style="float:right;"> 
    August 2018
    </span>
<br>PRESENTER</br>
</p>

*Poster*: Genetic Influences on Visual Aesthetic Preferences: Towards a New Etiological Perspective in Visual Empirical Aesthetics

<p style="text-align:left;">
    <strong>MA Workshop in brand and fashion design, Roma, Italy </strong>
    <span style="float:right;"> 
    Septermber 2017
    </span>
<br>SPEAKER</br>
</p>

*Talk*: Cognitive science and aesthetics, insights between boundaries;


## AWARDS

<p style="text-align:left;">
    <strong>VSAC 2019, Leuven, Belgium</strong>
    <span style="float:right;"> 
    August 2019
    </span>
<a href="https://www.researchgate.net/publication/335352770_Putting_Genetics_in_Aesthetics_Etiological_Sources_of_Variation_in_Aesthetic_Chills"><br>BEST POSTER AWARD</br></a>
</p>

<p style="text-align:left;">
    <strong>ERASMUS Plus</strong>
    <span style="float:right;"> 
    September 2016 - June 2018
    </span>
<br>SCHOLARSHIP</br>
</p>

<p style="text-align:left;">
    <strong>Mind & Machine, Amsetrdam, Netherlands</strong>
    <span style="float:right;"> 
    February 2017
    </span>
      </span>
<a href="https://giacomo673.wixsite.com/feelease"><br>BEST POSTER AWARD</br></a>
</p>

## PUBLICATIONS

<p style="text-align:left;">
    <strong>Research Gate</strong>
<a href="https://www.researchgate.net/publication/335352770_Putting_Genetics_in_Aesthetics_Etiological_Sources_of_Variation_in_Aesthetic_Chills"><br>ALL PUBLICATIONS</br></a>
</p>

Please, look at my Reserch Gate profile (Click [HERE](https://www.researchgate.net/profile/Giacomo_Bignardi2?ev=hdr_xprf&_sg=1xemDHvtq2DBEWPb0sHedHaAP_RPDFn7OdHcsGtBP-xZy4D0oaHkvH9oLhRq2plL8W5Diz1j5p6jDPf_jlxYU1Nh)). It is just easier. 

## EXTRACULLICURAR

{{< vimeo 316463576 >}}
<p style="text-align:left;">
    <strong> Generative Art  </strong>
    <span style="float:right;"> 
    January 2019 - ongoing
    </span>
  <a href="https://www.facebook.com/385058852329692/photos/ms.c.eJwtycEJADAMAsCNCklUdP~;FQkufx6FHlGAoqT54tlkjkt~;p~_zYW5~;kJtA~-~-.bps.a.423656635136580/423656928469884/?type=3&theater"> <br>EXHIBITION</br></a>
</p>

*Exhibition*: During my spare time I fool around, by doing some generative art. This is a video of on installation I did back in the days:

<p style="text-align:left;">
    <strong> Design </strong>
    <span style="float:right;"> 
    September 2017 - February 2018 ++
    </span>
  <a href="https://www.facebook.com/385058852329692/photos/ms.c.eJwtycEJADAMAsCNCklUdP~;FQkufx6FHlGAoqT54tlkjkt~;p~_zYW5~;kJtA~-~-.bps.a.423656635136580/423656928469884/?type=3&theater"> <br>DOC DESIGN</br></a>
</p>

*Design*: I worked, and still working for my family design companay. I mainly helped with the creation of the [website](https:://www.doc.design)






Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
